Finite-size study of the Quench Action approach in integrable spin chains

### 2015-07-31 draft/fs_qa.tex
fin

We numerically checked that the number of states with non-zero overlap 
with the Neel state is given as 
%
\begin{equation}
Z_N=2^{\frac{L}{2}-1}+\frac{1}{2}B\left(\frac{L}{2},
\frac{L}{4}\right)+1,
\end{equation}
%
with $B(x,y)$ denoting the binomial coefficient. The contribution $1$ 
accounts for the ferromagnetic state. Here 
we assumed that $L$ is divisible by four. Here $Z_N$ is be obtained 
as the total number of parity-invariant Bethe-Gaudin-Takahashi quantum 
numbers.

@@

>>>>

We numerically checked that the number of states with non-zero overlap 
with the Neel state is given as 
%
\begin{equation}
\label{Neel-count}
Z_N=2^{\frac{L}{2}-1}+\frac{1}{2}B\left(\frac{L}{2},
\frac{L}{4}\right)+1,
\end{equation}
%
with $B(x,y)$ denoting the binomial coefficient. The contribution $1$ 
accounts for the ferromagnetic state. Here 
we assumed that $L$ is divisible by four. Here $Z_N$ is be obtained 
as the total number of parity-invariant Bethe-Gaudin-Takahashi quantum 
numbers.

@@

%%%%%%%%%%%%%
\subsection{Proof of non-zero Neel overlap counting}

Here we prove~\eref{Neel-count}.

Let us consider the string configurations as before in which all the particle are 
distributed in at most $M/2$-strings, as ${\mathcal S}_{PI}=\{s_1,s_2,\dots,s_{M/2}\}$. 
Now we have $\sum_k ks_k=M$.

The number of available parity-invariant quantum numbers ${\mathcal N}_n$ in the 
$n$-string sector is now given as 
%
\begin{equation}
{\mathcal N}_n(L,{\mathcal S}_{PI})=\frac{L}{2}-\frac{1}{2}\sum_{m=1}^{M/2}t_{nm}s_m.
\end{equation}
%
